Avoiding accuracy-limiting pitfalls in the study of protein-ligand interactions with isothermal titration calorimetry

### 2015-07-14 manuscript/itc-worksheet.tex
Added thanks to Rockefeller HTSRC in Acknowledgments.

JDC acknowledges funding via a Distinguished Postdoctoral Fellowship from the California Institute for Quantitative Biosciences (QB3) at the University of California, Berkeley and from the Memorial Sloan Kettering Cancer Center during the course of this work.
SEB acknowledges support from QB3 during the performance of this work.
The authors are grateful to Brian K.~Shoichet (UCSF) for the use of his laboratory facilities for this study, as well as Allison Doak (UCSF) and Matthew Merski (UCSF) for their assistance.
The authors thank Patrick Grinaway, Daniel Parton, and Ari\"{e}n Sebastian Rustenburg (MSKCC) for stimulating the publication of this work through their subsequent work on this system.

>>>>

JDC acknowledges funding via a Distinguished Postdoctoral Fellowship from the California Institute for Quantitative Biosciences (QB3) at the University of California, Berkeley and from the Memorial Sloan Kettering Cancer Center during the course of this work.
SEB acknowledges support from QB3 during the performance of this work.
The authors are grateful to Brian K.~Shoichet (UCSF) for the use of his laboratory facilities for this study, as well as Allison Doak (UCSF) and Matthew Merski (UCSF) for their assistance.
The authors thank Patrick Grinaway, Daniel Parton, and Ari\"{e}n Sebastian Rustenburg (MSKCC) for stimulating the publication of this work through their subsequent work on this system, and Antonio Luz and Fraser Glickman (Rockefeller High-Throughput and Spectroscopy Resource Center) for their assistance and expertise with automated calorimetry.
